On proving things

### 2015-10-15 reasoning/huiswerk/inl1019.tex
started with 2a

\begin{scprooftree}{1}
	\AxiomC{$\Gamma \Rightarrow A, \Delta$}
	\AxiomC{$\Gamma, B \Rightarrow \Delta$}
	\BinaryInfC{$\Gamma, A \to B \Rightarrow \Delta$}
\end{scprooftree}

Let $V(x)$ be the valuation function that determines if sequent x
is true.

Let $\Gamma \Rightarrow A, \Delta$ be $P_1$,
let $\Gamma, B \Rightarrow \Delta$ be $P_2$ and
let $\Gamma, A \to B \Rightarrow \Delta$ be $C$

@@

The same technique can be applied for so we assume $V(\Gamma) = 0$ and $V(\Delta) = 1$.

\subsection{$R\to$}
\end{document}

>>>>

\begin{scprooftree}{1}
	\AxiomC{$\Gamma \Rightarrow A, \Delta$}
	\AxiomC{$\Gamma, B \Rightarrow \Delta$}
	\RightLabel{$L\to$}
	\BinaryInfC{$\Gamma, A \to B \Rightarrow \Delta$}
\end{scprooftree}

Let $V(x)$ be the valuation function that determines if sequent x
is true.
Let $\Gamma \Rightarrow A, \Delta$ be $P_1$,
let $\Gamma, B \Rightarrow \Delta$ be $P_2$ and
let $\Gamma, A \to B \Rightarrow \Delta$ be $C$

@@

The same technique can be applied for $V(\Gamma) = 0$ and $V(\Delta) = 1$.

There are no other valuations left, so if one of the premises of L $\to$ is
false then so is the conclusion

\subsection{$R\to$}
To proof that if one of the premises of $R\to$ of $GKC$ is not true
(under all valuations) than the conclusion not true either.

The definition of $R\to$ in $GKC$:

\begin{scprooftree}{1}
	\AxiomC{$\Gamma, A \Rightarrow B, \Delta$}
	\RightLabel{$R\to$}
	\UnaryInfC{$\Gamma \Rightarrow A \to B, \Delta$}
\end{scprooftree}
Let $V(x)$ be the valuation function that determines if sequent x
is true.
Let $\Gamma, A \Rightarrow B, \Delta$ be $P$ and
let $\Gamma \Rightarrow A \to B, \Delta$ be $C$

$V(P)$ can only be 0 if the result of
$V(\Gamma) \not= V(\Delta)$

If $V(\Gamma) = 1$, $V(A)$ also has to be 1 otherwise the premise would be true.
$V(B)$ has to be 0 because otherwise the premise would be true.

With these valuation $V(C)$ will be false.

The same result for $V(\Gamma) = 0$

There are no other valuations left, so if one of the premises of R $\to$ is
false then so is the conclusion

\section{Positivity and negativity}
\subsection{Prove C keeps occuring in premise and conclusion}
To prove that if formula $C$ occurs positively in one of the premises of a rule,
then the same formula occurs positively in the conclusion fro all rules of GKC

This will be done on a rule by rule basis.
\subsubsection{$R\wedge$}
Suppose C occurs positively in one of the premisses
($\Gamma \Rightarrow A, \Delta$) or ($\Gamma \Rightarrow B,\Delta$),
say in the first one. Thus it occurs positively in a formula in $\Delta$ or
$A$ or negatively in a formula in $\Gamma$. In the first and the last case,
the same holds for the conclusion ($\Gamma \Rightarrow A \wedge B, \Delta)$.
In case C occurs positively in $A$ then by definition it occurs positively
in $A \wedge B$ (even in the case that $C = A$). Hence it occurs positively
in ($\Gamma \Rightarrow A \wedge B, \Delta$). This is what had to be shown.

\end{document}
